Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling

### 2021-02-03 papers/intro_paper/intro.tex
a couple or more refs for intro

The observation of GWs has had significant astrophysical and cosmological
implications~\cite{TheLIGOScientific:2016htt,GBM:2017lvd,Monitor:2017mdv,Abbott:2017xzu}. It
has also allowed us to probe fundamental
physics and test predictions of Einstein's theory of General Relativity
(GR) in the previously unexplored highly-dynamical, and strong field
regime~\cite{TheLIGOScientific:2016src,Abbott:2018lct,LIGOScientific:2019fpa}. In GR, a binary black hole (BBH) system is described by
three distinct phases: an early \textit{inspiral}, where the two
compact objects spiral in loosing energy because of the emission of GWs, a \textit{merger} marked by the
formation of a common apparent horizon, and a \textit{ringdown}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs)~\cite{Vishveshwara:1970cc}\abhi{cite some of the other early QNM papers} (i.e., damped oscillations with specific, discrete frequencies and decay times).

@@

The first paper on tests of GR by the LIGO Collaboration~\cite{TheLIGOScientific:2016src} provided us with the
first measurement of the dominant damped-oscillation signal in the ringdown stage of a BBH
coalescence. The LIGO-Virgo O3a testing GR paper~\cite{Abbott:2020jks} has recently reported a comprehensive analysis of the properties of the remnant object, including the ringdown stage, for tens of GW events.
The no-hair conjecture in GR~\cite{Carter:1971zc,Hansen:1974zz} states that an (electrically neutral) astrophysical BH is completely
described by two observables: mass and spin angular momentum. One
consequence of the no-hair conjecture is that the (complex) QNM
frequencies of gravitational radiation emitted by a perturbed isolated
BH are uniquely determined by its mass and spin angular momentum. Hence
a test of the no-hair conjecture would involve checking for
consistency between estimates of mass and spin of the remnant object
across multiple QNM frequencies~\cite{Dreyer:2003bv}. An inconsistency would either
indicate a non-BH nature of the remnant object, or an incompleteness
of GR as the underlying theory of gravity.

>>>>

The observation of GWs has had significant astrophysical and cosmological
implications~\cite{TheLIGOScientific:2016htt,GBM:2017lvd,Monitor:2017mdv,Abbott:2017xzu}. It
has also allowed us to probe fundamental
physics and test predictions of Einstein's theory of General Relativity
(GR) in the previously unexplored highly-dynamical, and strong field
regime~\cite{TheLIGOScientific:2016src,Abbott:2018lct,LIGOScientific:2019fpa,Abbott:2020jks}. In GR, a binary black hole (BBH) system is described by
three distinct phases: an early \textit{inspiral}, where the two
compact objects spiral in loosing energy because of the emission of GWs, a \textit{merger} marked by the
formation of a common apparent horizon, and a \textit{ringdown}, during which the newly formed remnant object settles down to a Kerr BH emitting quasi-normal-modes (QNMs)~\cite{Vishveshwara:1970zz,Vishveshwara:1970cc,Teukolsky:1973ha,Press:1973zz,Chandrasekhar:1975zza,Detweiler:1980gk,Buonanno:2000ef,Pretorius:2005gq,Campanelli:2005dd,Baker:2005vv,Kokkotas:1999bd,Berti:2009kk}\abhi{cite some of the other early QNM papers}\rb{added a couple of important early QNM papers but also the NR breakthrough papers and Alessandra's paper on the transition form inspiral to plunge. } (i.e., damped oscillations with specific, discrete frequencies and decay times).

@@

The first paper on tests of GR by the LIGO Collaboration~\cite{TheLIGOScientific:2016src} provided us with the
first measurement of the dominant damped-oscillation signal in the ringdown stage of a BBH
coalescence, and more recently a similar measurement was made with the high-mass event GW190521~\cite{Abbott:2020tfl,Abbott:2020mjq}. This set of available measurements was greatly expanded in the latest LIGO-Virgo O3a testing GR paper~\cite{Abbott:2020jks} where a comprehensive analysis of the properties of the remnant object, including the ringdown stage, was reported for tens of GW events.\rb{slightly modified the previous two sentences to include also cite the GW190521 papers}
The no-hair conjecture in GR~\cite{Carter:1971zc,Hansen:1974zz} states that an (electrically neutral) astrophysical BH is completely
described by two observables: mass and spin angular momentum. One
consequence of the no-hair conjecture is that the (complex) QNM
frequencies of gravitational radiation emitted by a perturbed isolated
BH are uniquely determined by its mass and spin angular momentum. Hence
a test of the no-hair conjecture would involve checking for
consistency between estimates of mass and spin of the remnant object
across multiple QNM frequencies~\cite{Dreyer:2003bv}. An inconsistency would either
indicate a non-BH nature of the remnant object, or an incompleteness
of GR as the underlying theory of gravity.
